\documentclass[line, margin]{res}

\begin{document}
\name{\Huge \begin{flushleft}\ \ \ \ \ \ \ Alex Hoffer\end{flushleft}}
\address{2476 Bain CT SE\\ Albany, OR 97322\\ (541) 740-6700\\ hoffera@oregonstate.edu\\github.com/AlexDHoffer}

\begin{resume}
\section{OVERVIEW}
Entry level experience in all aspects of the software engineering process, from architectural design to refactoring and testing. Specific interests in human factors on both ends, such as software usability for end users and software maintainability for developers. \\

\section{EMPLOYMENT}
\textit{Undergraduate Researcher} at Oregon State University \hfill Spring 2016 - present \\
\begin{itemize}
\item Conduct research on home automation devices
\item Design, implement user survey
\item Perform data analysis on user surveys
\item Analyze network packets transferring from device to server
\item Write background and methods sections of academic publication
\end{itemize}

\section{EDUCATION}
Oregon State University \hfill Winter 2013 - present \\ 

\begin{itemize}
\item B.S. in Computer Science. In-major GPA: 3.70 
\item B.S. in Psychology. In-major GPA: 3.73
\item Coursework: Software Engineering I and II, Web Development, Operating Systems I and II, Mobile and Cloud Software Development, Programming Language Fundamentals, Theory of Computation, Usability Engineering, Open Source Software, Computer Architecture and Assembly Language \\
\end{itemize}

\section{PROJECTS}
\begin{itemize}
\item \textit{Instructional Machine Learning Module} (2016 - present). Online application where the user can choose a machine learning algorithm, their choice of college basketball statistics, and generate a March Madness bracket. HTML, CSS, JavaScript.
\item \textit{Testing a URL Validator} (2016). Writing test cases to verify the accuracy of a URL Validator application. Java, JUnit.
\item \textit{Mental Illness Forum} (2016). Online discussion board where recovering drug addicts can register, log in, and post about recovery. HTML, CSS, JavaScript, MySQL.
\item \textit{Firefighter Scheduler} (2016). Online application where firefighters of Tanget, OR can register, log in, and change their work schedule. HTML, CSS, JavaScript, MySQL.
\end{itemize}

\section{LANGUAGES}
\begin{itemize}
\item C/C++, Java, Python, MySQL, HTML, CSS, PHP, Bash Shell Scripting, JavaScript, Microsoft Macro Assembler (MASM), R, LaTeX, Haskell \\
\end{itemize}

\section{TECHNOLOGIES}
\begin{itemize}
\item Microsoft Visual Studio, Vim, Notepad++, Git, Github, Mockito, JUnit \\
\end{itemize}

\end{resume}
\end{document}
